\documentclass[12pt,a4paper]{article}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{margin=1in}

\begin{document}

\begin{center}
    {\Large \textbf{Experiment 2: Plagiarism Detection using A*}} \\
    \vspace{0.5cm}
    Manoj Kumar Panda -- 20251602013 \\
    Meetkumar Kankotiya -- 20251602007 \\
    Shrey Parikh -- 20251602017 \\
    CS663 -- Artificial Intelligence \\
\end{center}

\section*{Abstract}
This experiment implements plagiarism detection between two text documents by aligning their sentences using the A* search algorithm with edit distance as the alignment cost.

\section*{Problem Formulation}
We treat two documents as sequences of sentences:
\begin{itemize}
    \item \textbf{State:} A pair $(i,j)$, where $i$ and $j$ are indices into the two sentence sequences.
    \item \textbf{Initial State:} $(0,0)$ (start of both documents).
    \item \textbf{Goal State:} $(n,m)$, where $n$ and $m$ are the number of sentences.
    \item \textbf{Actions:} Align sentences, skip a sentence in Document~1, or skip a sentence in Document~2.
    \item \textbf{Cost:} Levenshtein distance for aligning two sentences, or a fixed penalty for skipping.
\end{itemize}

\section*{Algorithm}
We apply the A* search algorithm with evaluation function:
\[
f(n) = g(n) + h(n)
\]
where $g(n)$ is the accumulated cost. For this experiment, we use $h(n)=0$ to guarantee admissibility.

\section*{Implementation}
The full Python implementation is available at the online compiler:

\begin{center}
\Large \url{https://github.com/mkankotiya/AI-CS659/commit/38efb83e28796fb5ce065097dc44e4bfed774fcf}
\end{center}

\section*{Results}
The program prints the alignment cost and aligned sentences. 
\begin{itemize}
    \item Identical documents $\rightarrow$ cost = 0.  
    \item Slightly modified documents $\rightarrow$ low cost.  
    \item Different documents $\rightarrow$ high cost.  
\end{itemize}

\section*{Discussion}
This approach works well for small to medium documents. For large texts, runtime can be reduced by better heuristics or semantic similarity measures.

\section*{Conclusion}
The A* algorithm with edit distance provides a clear and interpretable method for detecting plagiarism and aligning textual data.

\end{document}
